\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-07-28 paper/paper.tex
Add figure (nonparametric summaries of DM 14) to paper

@@

\newcommand{\ind}{\stackrel{ind.}{\sim}}
\newcommand{\op}{\operatorname}

\newcommand{\myequation}{\begin{equation}}
\newcommand{\myendequation}{\end{equation}}
\let\[\myequation
\let\]\myendequation

@@

The prior on $\pi$ implies with $90\%$ probability $\pi$ is in the interval $(.002, .572)$.  Given the interpretation of $\pi$ as the proportion of defective units, which we would expect to be small, a range primarily covering the left side of 0.50 is reasonable and weakly informative.  The prior on $\sigma_1$ and $\sigma_2$ put the majority of mass on the interval $(0.02, 61.1)$ with $90\%$ probability.  Again, this allows for a wide range of hazards, larger than we would expect to see in the data.  The $t_{0.5,1}$ distribution has a prior $90\%$ interval of $(1.4,14.6)$. For $t_{0.2,2}$ the range is $(3.4,16.6)$. Since these last two parameters are on the scale of log-hours, admitting values from hours to decades, we consider them to be relatively uninformative.  They do, however, help separate the early and late failure modes--the earlier infant mortality mode having a lower mean time to failure than the wearout mode.  This is helpful for estimation since, as discussed in Chan & Meeker, ML had difficulty identifying the two sets of GLFP parameters without making strong assumptions about the data.  \\

>>>>

% no longer require relative path to figs
\graphicspath{{fig/}}

@@

\newcommand{\ind}{\stackrel{ind.}{\sim}}
\newcommand{\op}{\operatorname}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\myequation}{\begin{equation}}
\newcommand{\myendequation}{\end{equation}}
\let\[\myequation
\let\]\myendequation

@@

\begin{figure}[H]
\centering
\includegraphics{np_ex1}
\caption{Top: Lifetime plot of data from 75 randomly selected units of drive-model `14'. Bottom: Kaplan-Meier estimate for drive-model `14'.}
\label{dm14}
\end{figure}
The prior on $\pi$ implies with $90\%$ probability $\pi$ is in the interval $(.002, .572)$.  Given the interpretation of $\pi$ as the proportion of defective units, which we would expect to be small, a range primarily covering the left side of 0.50 is reasonable and weakly informative.  The prior on $\sigma_1$ and $\sigma_2$ put the majority of mass on the interval $(0.02, 61.1)$ with $90\%$ probability.  Again, this allows for a wide range of hazards, larger than we would expect to see in the data.  The $t_{0.5,1}$ distribution has a prior $90\%$ interval of $(1.4,14.6)$. For $t_{0.2,2}$ the range is $(3.4,16.6)$. Since these last two parameters are on the scale of log-hours, admitting values from hours to decades, we consider them to be relatively uninformative.  They do, however, help separate the early and late failure modes--the earlier infant mortality mode having a lower mean time to failure than the wearout mode.  This is helpful for estimation since, as discussed in Chan \& Meeker, ML had difficulty identifying the two sets of GLFP parameters without making strong assumptions about the data.  \\
